---
title: "LIWC"
author: "Ignacio Ojea"
date: "21 December 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

Load required packages (install first if necessary):

```{r cars}
require(readtext)
# require(LIWClike)
library("quanteda.dictionaries")
require(quanteda)
require(dplyr)
require(tidytext)
```

## Read into R and transform into a corpus:

You can also embed plots, for example:

```{r pressure, echo=FALSE}
covidtweetsfull <- readtext("~/Dropbox/covidtweets/full/*")
covidtweetspre <- readtext("~/Dropbox/covidtweets/pre/*")
covidtweetspost <- readtext("~/Dropbox/covidtweets/post/*")
covidtweetsfull_corpus <- corpus(covidtweetsfull)
covidtweetspre_corpus <- corpus(covidtweetspre)
covidtweetspost_corpus <- corpus(covidtweetspost)
```

## Tokenize the corpus, remove punctuation:

```{r}
dfmat_covidtweetsfull <- dfm(covidtweetsfull_corpus, stem = FALSE, remove_punct = TRUE)
dfmat_covidtweetspre <- dfm(covidtweetspre_corpus, stem = FALSE, remove_punct = TRUE)
dfmat_covidtweetspost <- dfm(covidtweetspost_corpus, stem = FALSE, remove_punct = TRUE)
```

## Hierarchical Clustering

Hierarchical clustering to establish the pairwise similarity of all corpora, then plot the results as a dendrogram:

```{r}
tstat_dist <- textstat_dist(dfm_weight(dfmat_covidtweetsfull, scheme = "prop"))
covid_cluster <- hclust(as.dist(tstat_dist))
covid_cluster$labels <- docnames(dfmat_covidtweetsfull)
plot(covid_cluster, xlab = "", sub = "",
     main = "Euclidean Distance on Normalized Token Frequency")
 
tstat_dist <- textstat_dist(dfm_weight(dfmat_covidtweetspre, scheme = "prop"))
covid_cluster <- hclust(as.dist(tstat_dist))
covid_cluster$labels <- docnames(dfmat_covidtweetspre)
plot(covid_cluster, xlab = "", sub = "",
     main = NULL)
 
tstat_dist <- textstat_dist(dfm_weight(dfmat_covidtweetspost, scheme = "prop"))
covid_cluster <- hclust(as.dist(tstat_dist))
covid_cluster$labels <- docnames(dfmat_covidtweetspost)
plot(covid_cluster, xlab = "", sub = "",
     main = NULL)
```

## MFT

Pass through Moral Foundations Theory dictionary via liwcalike:

```{r}
mft <- dictionary(file = "mft.dic")
LIWCanalysismft <- liwcalike(covidtweets_corpus, mft)
LIWCanalysismft
write.csv(LIWCanalysismft, file = "covid_mft.csv")
```

## MAC

Pass through morality-as-cooperation virtue and vice dictionaries:

```{r}
macdvirtue <- dictionary(file = "macdvirtue.dic")
LIWCanalysisvirtue <- liwcalike(covidtweets_corpus, macdvirtue)
LIWCanalysisvirtue
write.csv(LIWCanalysisvirtue, file = "covid_macdvirtue.csv")

macdvice <- dictionary(file = "macdvice.dic")
LIWCanalysisvice <- liwcalike(covidtweets_corpus, macdvice)
LIWCanalysisvice
write.csv(LIWCanalysisvice, file = "covid_macdvice.csv")
```


## Basic LIWC

```{r}
basicliwc <- dictionary(file = "liwcdict.dic")
LIWCanalysisbasic <- liwcalike(covidtweets_corpus, basicliwc)
LIWCanalysisbasic
write.csv(LIWCanalysisbasic, file = "covid_liwc.csv")
```

```{r}
covidmoralspre <- read.csv("covidmoralspre.csv")
covidmoralspost <- read.csv("covidmoralspost.csv")
covid_label <- covidmoralspre$docname
covidmoralspre_df <- covidmoralspre[,2:18]
covidmoralspost_df <- covidmoralspost[,2:18]
covidmoralspre_df_sc <- as.data.frame(scale(covidmoralspre_df))
covidmoralspost_df_sc <- as.data.frame(scale(covidmoralspost_df))
dist_matpre <- dist(covidmoralspre_df_sc, method = "euclidean")
dist_matpost <- dist(covidmoralspost_df_sc, method = "euclidean")
```